\documentclass[a4paper]{article}

% if you need to pass options to natbib, use, e.g.:
%     \PassOptionsToPackage{numbers, compress}{natbib}
% before loading neurips_2022


% ready for submission
%\usepackage{ofu_xai_2022}

\input{math_commands.tex}

% to compile a preprint version, e.g., for submission to arXiv, add add the
% [preprint] option:
%     \usepackage[preprint]{ofu_xai_2022}


% to compile a camera-ready version, add the [final] option, e.g.:
\usepackage[final, nonatbib]{ofu_xai_2022}

% to avoid loading the natbib package, add option nonatbib:
%    \usepackage[nonatbib]{ofu_xai_2022}


\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage[hidelinks,allcolors=black]{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{xcolor}         % colors
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{caption}
\usepackage[round]{natbib}
%%%%

\usepackage{listings}
\usepackage{xcolor}
\usepackage{adjustbox}

\usepackage[linesnumbered,ruled,vlined]{algorithm2e}

\definecolor{codegray}{gray}{0.95}

\lstdefinestyle{mystyle}{
	backgroundcolor=\color{codegray},
	commentstyle=\color{green!50!black},
	keywordstyle=\color{blue},
	numberstyle=\tiny\color{gray},
	stringstyle=\color{orange},
	basicstyle=\ttfamily\footnotesize,
	breaklines=true,
	captionpos=b,
	keepspaces=true,
	numbers=left,
	numbersep=5pt,
	showspaces=false,
	showstringspaces=false,
	showtabs=false,
	tabsize=2
}

\lstset{style=mystyle}

\title{Project Report}


% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to LaTeX to determine where to break the
% lines. Using \AND forces a line break at that point. So, if LaTeX puts 3 of 4
% authors names on the first line, and the last on the second line, try using
% \AND instead of \And before the third author name.


\author{%
 Maximilian Emmanuel Rittler, Johannes Christian Schuster, Hannes Christian Weber %\thanks{Use footnote for providing further information
    %about author (webpage, alternative address)} \\
    \\
  Otto-Friedrich University of Bamberg\\
  96049 Bamberg, Germany\\
  \href{mailto:maximilian-emmanuel.rittler@stud.uni-bamberg.de}{\texttt{maximilian-emmanuel.rittler@stud.uni-bamberg.de}} \\
  \href{mailto:johannes-christian.schuster@stud.uni-bamberg.de}{\texttt{johannes-christian.schuster@stud.uni-bamberg.de}}
   \\
   \href{mailto:hannes-christian.weber@stud.uni-bamberg.de}{\texttt{hannes-christian.weber@stud.uni-bamberg.de}}\\[0.5cm]
  xAI-Proj-M: Domain Generalization \\
  Degree: M.Sc. AI
  % examples of more authors
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \AND
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
}


\begin{document}


\maketitle
\def\va{{\bm{a}}}

\begin{abstract}
	This project addresses the challenge of domain generalization, which involves training models that generalize effectively to unseen target domains without access to target data during training. To this end, we implement and evaluate the MixStyle method, a feature-space data augmentation technique designed to mitigate domain shift by perturbing style statistics within intermediate network layers. Experimental evaluations are conducted on two benchmark datasets of varying scale - PACS (small-scale) and Office-Home (large-scale) - to assess the robustness and effectiveness of MixStyle under different data regimes. The empirical results demonstrate that MixStyle consistently enhances generalization performance across domains, with particularly notable gains in low-data scenarios. These findings highlight the potential of MixStyle as a lightweight yet effective approach for improving model robustness in domain generalization settings.
\end{abstract}
\clearpage
\input{introduction.tex}

\input{related_work.tex}
\input{methods.tex}
\input{experimental_setup.tex}
\input{experiments.tex}
\input{discussion.tex}
\input{conclusion.tex}


\section{Notation}
\input{math_notation.tex}

\medskip



\bibliography{xAI-Proj}
\bibliographystyle{abbrvnat}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Declaration of Authorship
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\parindent 0cm
%%%%%%%%%%%%%%%%%%%%%%%%%%German%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Declaration of Authorship}
Ich erkläre hiermit gemäß § 9 Abs. 12 APO, dass ich die vorstehende Seminararbeit selbstständig verfasst und keine anderen als die angegebenen Quellen und Hilfsmittel benutzt habe. Des Weiteren erkläre ich, dass die digitale Fassung der gedruckten Ausfertigung der Seminararbeit ausnahmslos in Inhalt und Wortlaut entspricht und zur Kenntnis genommen wurde, dass diese digitale Fassung einer durch Software unterstützten, anonymisierten Prüfung auf Plagiate unterzogen werden kann.\\
\vspace{2\baselineskip}
  
Bamberg, \today

\rule[0.5em]{14em}{0.5pt} \hspace{0.25\linewidth}\rule[0.5em]{14em}{0.5pt}
\vspace{1em}
\hspace{4em} (Ort, Datum) \hspace{0.51\linewidth} (Unterschrift)
}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\appendix


\section{Appendix}


Optionally include extra information (complete proofs, additional experiments and plots) in the appendix.
This section will often be part of the supplemental material.


\end{document}
